---
title: "Excess death in Mexico City and NYC"
author: "Dan Weinberger"
date: "9/21/2020"
output:
  html_document:
    df_print: paged
    html_document: null
    toc: yes
    toc_depth: 2
    toc_float: yes
  word_document:
    toc: yes
    toc_depth: '2'
  pdf_document: 
    keep_tex:  true
params:
  agg.level: 'state'
  n.days.filter: 20
  web.version: FALSE
  extrap.date: '2020-01-26'
  count.start.date: '2020-03-01'
  end.data.date: '2020-09-05'
---

```{r, include = F}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo=F,
  warning=FALSE, 
  message=FALSE,
  comment = "#>",
  dev=c('png','pdf'),
  fig.path='./figures/',
  gganimate = list(
    nframes = 50)
)

extrap.date <-  as.Date(params$extrap.date)
count.start.date <- as.Date(params$count.start.date)
end.data.date <- as.Date(params$end.data.date)

state.name2 <- c(state.name, 'District of Columbia','Puerto Rico', 'United States', 'New York City')
state.abb2 <- c(state.abb, 'DC','PR','US','NYC')


last.date.format <- 
  format(end.data.date, '%b %d, %Y')
```

```{r setup}
library(ExcessILI)
library(cdcfluview)
library(reshape2)
library(ggplot2)
library(lubridate)
library(RColorBrewer)
library(plotly)
library(MMWRweek)
library(readr)
library(rjson)
library(htmlTable)
library(RSocrata)
library(pdftools)
library(readr)
library(abind)
library(gsubfn)
library(dplyr)
library(RCurl)
library(gifski)
library(gganimate)
#library(jsonlite)
set.seed(123)
source('./functions/ts_plot_func.R')
source('./functions/format_table.R')
source('./functions/stack_plot.R')

```

```{r archivfunc}
# Using ExcessILI's data archiving functions, returns the most recent copy of
# output obtained by running a function or formula \code{f}, unless this 
# copy doesn't exist or is older (by modification time) than \code{maxage}.
# In that case, \code{f} is run and the output is archived into the folder
# Data/'storeName' as an RDS file, using the function ExcessILI::storeRDS.
#
# @param storeName A string. The name of the folder to store output in
# @param f A function or formula taking no arguments. Formulas are coerced to
#   functions.
# @param maxage How old can any existing archived file be before \code{f} is 
#   called again?
runIfExpired <- function(storeName, f, maxage=hours(99999999999999)) {
  basepath <- "Data/"
  mostRecent <- mostRecentTimestamp(storeName, basepath=basepath)
  f <- rlang::as_function(f)
  
  runAndArchive <- function() {
    data <- f()
    storeRDS(data, storeName, basepath)
    data
  }
    
  if (is.na(mostRecent)) 
    return(runAndArchive())

  if (mostRecent %--% now() < maxage)
    return(retrieveRDS(storeName, basepath))

  runAndArchive()
}
```

```{r, eval=F}
if (!require("devtools")) {
  install.packages("devtools")
}
devtools::install_github("weinbergerlab/ExcessILI")
```

```{r}
nchs.base1.data <-
  read.csv('./Data/nchs_base1_data/Weekly_Counts_of_Deaths_by_State_and_Select_Causes__2014-2018.csv')

nchs.base1.data <-
  nchs.base1.data[,c("Jurisdiction.of.Occurrence","MMWR.Year" ,"MMWR.Week" , "Week.Ending.Date","All..Cause","flag_allcause")]

names(nchs.base1.data) <-c('state', 'year','week','week_end','all_cause', 'flag_ac')

csv.url <- "https://data.cdc.gov/api/views/r8kw-7aab/rows.csv?accessType=DOWNLOAD"
ds.func <- function(url){
  ds1<- read.csv("https://data.cdc.gov/api/views/r8kw-7aab/rows.csv?accessType=DOWNLOAD") 
return(ds1)
  }

nchs.base2.data <- runIfExpired('nchs_base2_data', 
 ~read.csv("https://data.cdc.gov/api/views/muzy-jte6/rows.csv?accessType=DOWNLOAD") 
 )

nchs.base2.data <- nchs.base2.data[,c("Jurisdiction.of.Occurrence" ,"Week.Ending.Date" ,"All.Cause")]

names(nchs.base2.data) <- c("State","week_end", 'Total.Deaths'  )

nchs.base2.data$Total.Deaths <-
  as.numeric(nchs.base2.data$Total.Deaths)

names(nchs.base2.data) <-c('state', 'week_end','all_cause')

nchs.base2.data$week_end <- as.Date(nchs.base2.data$week_end, '%Y-%m-%d')


nchs.base2.data$all_cause <-
  as.numeric(nchs.base2.data$all_cause)

nchs.base1.data$week_end <-
  as.Date(nchs.base1.data$week_end, '%m/%d/%Y')

nchs.base.comb <-
  bind_rows(nchs.base1.data,nchs.base2.data)

#Import the cdcfluview data
pi.data <- runIfExpired('pi_mortality_state', ~pi_mortality(coverage_area='state'))

pi.data <- pi.data[pi.data$coverage_area=='state',c('week_end','all_deaths' ,'region_name')]
names(pi.data) <-c('week_end',"all_deaths",'region_name')

fluview <- pi.data

```

Restrict to NYC
```{r}

nyc.fluview <- fluview[fluview$region_name=='New York City',]
nyc.fluview <-
  nyc.fluview[order(nyc.fluview$week_end),]
nyc.fluview$state <- 'NYC_loc_res'
nyc.fluview <- nyc.fluview[,c('state','week_end', 'all_deaths')]
names(nyc.fluview) <- c('state','week_end', 'all_cause')

nyc.nchs <- nchs.base.comb[nchs.base.comb$state=='New York City',]
nyc.nchs$state <- 'NYC_loc_death'
nyc.nchs <- nyc.nchs[,c('state','week_end', 'all_cause')]
#plot(nyc.nchs$week_end, nyc.nchs$all_cause)
```

NYC age
```{r}
#https://data.cdc.gov/NCHS/Weekly-counts-of-deaths-by-jurisdiction-and-age-gr/y5bj-9g5w/
#by jurisdiction of occurrence

ny.age1 <- read.csv('./Data/nchs_age/Weekly_counts_of_deaths_by_jurisdiction_and_age_group.csv')
ny.age1 <- ny.age1[ny.age1$State.Abbreviation=='YC' & ny.age1$Type=='Unweighted',]
ny.age1 <- ny.age1[,c('Week.Ending.Date', 'Age.Group','Number.of.Deaths' )]
ny.age1$Week.Ending.Date <- as.Date(ny.age1$Week.Ending.Date, '%m/%d/%Y')
ny.age1$agegroup2 <- NA
ny.age1$agegroup2[ny.age1$Age.Group %in% c('Under 25 years','25-44 years')] <- "00-44Y"
ny.age1$agegroup2[ny.age1$Age.Group %in% c('45-64 years')] <- "45-64Y"
ny.age1$agegroup2[ny.age1$Age.Group %in% c('65-74 years','75-84 years','85 years and older' )] <- "65+Y"
ny.age1$state <- paste0('NYC_loc_death_', ny.age1$agegroup2)
ny.age2 <- aggregate(ny.age1[,c('Number.of.Deaths'), drop=F],
                     by=list('state'=ny.age1$state,'week_end'=ny.age1$Week.Ending.Date), FUN=sum)
names(ny.age2) <-c('state','week_end','all_cause')

```


Mexico data
```{r}
#this is same as the disaggregated data below

# mx1 <- read.csv('./Data/Mx/cdmx_ts_format.csv')
# mx1$state <- 'MXC_all'
# mx1$DATE <- as.Date(mx1$DATE)
# mx1$week_end <- floor_date(mx1$DATE, unit='week')+6
# mx2 <- aggregate(mx1$DEATH, by=list('week_end'=mx1$week_end, 'state'=mx1$state), FUN=sum)
# mx2 <- mx2[,c('state','week_end','x')]
# names(mx2) <- c('state','week_end', 'all_cause')
```

Mexico, age stratified
```{r}
mx1.age <- read.csv('./Data/Mx/cdmx_age_ts_format.csv')
mx1.age$state <- paste0('MXC_res_', mx1.age$agegrp)
mx1.age <- mx1.age[mx1.age$RESIDENCY_STATE=='CDMX',]
mx1.age$DATE <- as.Date(mx1.age$DATE)
mx1.age$week_end <- floor_date(mx1.age$DATE, unit='week')+6
mx2.age <- aggregate(mx1.age$DEATH, by=list('week_end'=mx1.age$week_end, 'state'=mx1.age$state), FUN=sum)
mx2.age <- mx2.age[,c('state','week_end','x')]
names(mx2.age) <- c('state','week_end', 'all_cause')

```

MX all ages, by residency
```{r}
mx1.all.res <- mx1.age
mx1.all.res$state <- 'MXC_res'
mx2.all.res <- aggregate(mx1.all.res$DEATH, by=list('week_end'=mx1.all.res$week_end,'state'=mx1.all.res$state), FUN=sum)
mx2.all.res <- mx2.all.res[,c('state','week_end','x')]
names(mx2.all.res) <- c('state','week_end', 'all_cause')
```

MX all ages, by loc of death
```{r}
mx1.all <- read.csv('./Data/Mx/cdmx_age_ts_format.csv')
mx1.all$DATE <- as.Date(mx1.all$DATE)
mx1.all$week_end <- floor_date(mx1.all$DATE, unit='week')+6
mx1.all.loc <- mx1.all
mx1.all.loc$state <- 'MXC_loc_death'
mx2.all.loc <- aggregate(mx1.all.loc$DEATH, by=list('week_end'=mx1.all.loc$week_end,'state'=mx1.all.loc$state), FUN=sum)
mx2.all.loc <- mx2.all.loc[,c('state','week_end','x')]
names(mx2.all.loc) <- c('state','week_end', 'all_cause')
```


## Combine the datasets
```{r}

ds.comb <- rbind.data.frame(mx2.all.res,mx2.all.loc,mx2.age,nyc.nchs, nyc.fluview,ny.age2)
ds.comb$one <- 1
ds.comb <- ds.comb[ds.comb$week_end >= as.Date('2017-01-08') & ds.comb$week_end <= as.Date('2020-08-31') ,]

ds.comb <- ds.comb[order(ds.comb$state, ds.comb$week_end),]
```


## run the model
```{r}

mod1 <- excessCases(ds.comb, 
             statevar = "state",
             datevar = "week_end", 
             use.syndromes = c("all_cause"),
            extrapolation.date = as.Date("2020-03-01"), 
            sum.dates = as.Date("2020-03-01"),
            denom.var = "one",
            extend.epiyear =TRUE,
            time.res='week',
            model.type='negbin') 
```
 Extract output
```{r}
ds <- mod1
dates1 <-
  ds[[1]][[1]][[1]]$date
  
sum.obs.ac <-
    excessExtract(ds = ds,
                syndrome = 'all_cause',
                extract.quantity = "sum.obs")

sum.obs.ac2 <- apply(sum.obs.ac,2, sum)

denom.check <-
    excessExtract(ds = ds,
                syndrome = 'all_cause',
                extract.quantity = "denom")

dispersion <-
    excessExtract(ds = ds,
                syndrome = 'all_cause',
                extract.quantity = "disp")

##National data is created by summing state data
sum.pred.iter.ac <-    
  excessExtract(ds = ds,
                syndrome = 'all_cause',
                extract.quantity = "sum.pred.iter")

excess.grp <- matrix(NA, nrow=dim(sum.pred.iter.ac)[1], ncol=length(sum.obs.ac2))

for(i in 1:length(sum.obs.ac2)){
 excess.grp[,i] <-  sum.obs.ac2[i] - sum.pred.iter.ac[,i,1]
}
excess.grp.q <- t(apply(excess.grp,2, quantile, probs=c(0.025,0.5, 0.975)))
excess.grp.q <- cbind.data.frame('group'=dimnames(sum.obs.ac)[[2]],excess.grp.q)

ac.nat.obs <-    
  excessExtract(ds = ds,
                syndrome = 'all_cause',
                extract.quantity = "y")
ac.nat.obs <- ac.nat.obs[,dimnames(ac.nat.obs)[[2]]!='US',1]

pred.iter.ac <-    
  excessExtract(ds = ds,
                syndrome = 'all_cause',
                extract.quantity = "pred.iter")

pred.iter.ac2 <- array(pred.iter.ac,dim=c(length(dates1),10000,dim(pred.iter.ac)[2],1 ))

dimnames(pred.iter.ac2)[[3]] <- dimnames(pred.iter.ac)[[2]]

pred.ac.q <- apply(pred.iter.ac2, c(1,3), quantile, probs=c(0.025, 0.5, 0.975))


#excessN.iter <- sum.pred.iter.ac

```

## Summary of excess deaths March 1-Aug 29
```{r}
excess.grp.q.rd <- excess.grp.q
excess.grp.q.rd[,-1] <- apply(excess.grp.q[-1],2, function(x) round(x,-2))

outtab1 <- paste0(excess.grp.q.rd[,3], ' (', excess.grp.q.rd[,2],', ', excess.grp.q.rd[,4],')' )
outtab1 <- cbind.data.frame(excess.grp.q.rd[,1],outtab1)
htmlTable(outtab1)
```

## Compare NYC and MXC, based on location of death
```{r}
plot(dates1,pred.ac.q['50%',,'MXC_loc_death'], bty='l',type='l', col='red', ylim=c(0, 8000), lty=2, ylab='Deaths(N)')
polygon(c(dates1, rev(dates1)), c(pred.ac.q['2.5%',,'MXC_loc_death'], rev(pred.ac.q['97.5%',,'MXC_loc_death'])),border=NA, col=rgb(1,0,0,alpha=0.2) )
points(dates1, ac.nat.obs[,'MXC_loc_death'], type='l', col='red')

#Overlay NYC
polygon(c(dates1, rev(dates1)), c(pred.ac.q['2.5%',,"NYC_loc_death"], rev(pred.ac.q['97.5%',,"NYC_loc_death"])),border=NA, col=rgb(0,0,1,alpha=0.2) )
points(dates1, ac.nat.obs[,"NYC_loc_death"], type='l', col='blue')
points(dates1, pred.ac.q['50%',,"NYC_loc_death"], col='blue', lty=2, type='l')

```

## Compare NYC and MXC, based on residence.
Important note: for NYC, if someone dies in another state but is resident in NYC, it will get added to NYC total. Not sure if same is true in MX data
```{r}
plot(dates1,pred.ac.q['50%',,'MXC_res'], bty='l',type='l', col='red', ylim=c(0, 8000), lty=2, ylab='Deaths(N)')
polygon(c(dates1, rev(dates1)), c(pred.ac.q['2.5%',,'MXC_res'], rev(pred.ac.q['97.5%',,'MXC_res'])),border=NA, col=rgb(1,0,0,alpha=0.2) )
points(dates1, ac.nat.obs[,'MXC_res'], type='l', col='red')

#Overlay NYC
polygon(c(dates1, rev(dates1)), c(pred.ac.q['2.5%',,"NYC_loc_res"], rev(pred.ac.q['97.5%',,"NYC_loc_res"])),border=NA, col=rgb(0,0,1,alpha=0.2) )
points(dates1, ac.nat.obs[,"NYC_loc_res"], type='l', col='blue')
points(dates1, pred.ac.q['50%',,"NYC_loc_res"], col='blue', lty=2, type='l')

```


## reshap to year*week
```{r}

mmw1 <- MMWRweek(ds.comb$week_end)
ds.comb <- cbind.data.frame(ds.comb, mmw1)

obs.m <- melt(ds.comb[,c('state', 'all_cause',"MMWRyear", "MMWRweek")], id.vars =c('state', "MMWRyear", "MMWRweek") )
obs.c <- acast(obs.m, state ~  MMWRyear ~ MMWRweek )
```


```{r}
col1 <- '#e41a1c'
col1.t <- '#e41a1c4D'
col2 <- '#377eb8'
col2.t <- '#377eb84D'
```

Panels
```{r}

par(mfrow=c(2,2))

groups.to.test<- list(
  c('MXC_res', 'NYC_loc_death'),
  c('MXC_res_00-44Y', 'NYC_loc_death_00-44Y'),
  c('MXC_res_45-64Y', 'NYC_loc_death_45-64Y'),
  c('MXC_res_65+Y', 'NYC_loc_death_65+Y')
)

lab1 <- c('All ages','0-44y','45-64y','65+y')

denoms <- list(
  c(9031213,8398748),
  c(5872023,5096607),
  c(2194170,2056048),
  c(965020,1246093)
)

#Panel A

for(i in c(1:4)){
  yrange <- range( c(obs.c[groups.to.test[[i]][1],c('2020'),]/denoms[[i]][1]*100000, obs.c[groups.to.test[[i]][2],c('2020'),]/denoms[[i]][2]*100000), na.rm=T )
matplot(t(obs.c[groups.to.test[[i]][1],c('2017','2018','2019'),])/denoms[[i]][1]*100000, bty='l',type='l', col=col1.t, 
        ylim=c(0, yrange[2]),
        xlim=c(1,35),
        lty=1, ylab='Deaths(N)', main=lab1[i])
points(obs.c[groups.to.test[[i]][1],c('2020'),]/denoms[[i]][1]*100000, type='l', col=col1, lty=1, lwd=2)

matplot(t(obs.c[groups.to.test[[i]][2],c('2017','2018','2019'),])/denoms[[i]][2]*100000, bty='l',type='l', col=col2.t,  lty=1, ylab='Deaths(N)', add=T)
points(obs.c[groups.to.test[[i]][2],c('2020'),]/denoms[[i]][2]*100000, type='l', col=col2, lty=1, lwd=2)

}



```





